Computing Entropies With Nested Sampling

### 2017-03-18 paper/ms.tex
Writing about NS

Nested Sampling \citep[NS][]{skilling2006nested} is an algorithm whose aim is
to calculate the marginal likelihood
\begin{align}
Z &= \int \pi(\x) L(\x) \, d\x
\end{align}
where $\x$ is the unknown parameter(s), $\pi$ is the prior distribution,
and $L$ is the likelihood function. It does this evolving a population of
$N$ particles in the parameter space.

Defining $X(\ell)$ as the amount of prior mass with likelihood greater than
some threshold $\ell$,
\begin{align}
X(\ell) &= \int \pi(\x) \mathds{1}\left(L(\x) > \ell\right) \, d\x,
\end{align}

The $N$ particles are initially initialised from the prior $\pi(\x)$, and the
particle with the lowest likelihood.

@@

Given the definition of the NS algorithm,
the probability distribution for the proportion $t$ of the prior mass
retained on a given iteration is
\begin{align}
t_i &\sim \textnormal{Beta}(N, 1),
\end{align}
and the probability distribution for the sequence of $X$-values is
obtained from
\begin{align}
X_i &= \prod_{k=1}^i t_i.
\end{align}

>>>>

Nested Sampling \citep[NS][]{skilling2006nested} is an algorithm whose aim is
to calculate the marginal likelihood
\begin{align}
Z &= \int \pi(\x) L(\x) \, d\x
\end{align}
where $\x$ is the unknown parameter(s), $\pi$ is the prior distribution,
and $L$ is the likelihood function. It does this evolving a population of
$N$ particles in the parameter space.
Defining $X(\ell)$ as the amount of prior mass with likelihood greater than
some threshold $\ell$,
\begin{align}
X(\ell) &= \int \pi(\x) \mathds{1}\left(L(\x) > \ell\right) \, d\x,
\end{align}

The $N$ particles are initially initialised from the prior $\pi(\x)$, and the particle with the lowest likelihood is found.
{\todo Write more here}

@@

Given the definition of the NS algorithm,
the probability distribution for the proportion $t$ of the prior mass
retained on a given iteration is
\begin{align}
t_i &\sim \textnormal{Beta}(N, 1),
\end{align}
and the probability distribution for the sequence of $X$-values of
the discarded points is obtained from
\begin{align}
X_i &= \prod_{k=1}^i t_i.
\end{align}
The corresponding likelihood values of the discarded points are
denoted $L_1, L_2, L_3$, and so on.

Consider a particular likelihood value $\ell$ whose $X$-value
we would like to know.
The number of discarded points with likelihood below $\ell$, i.e.,
the number of NS iterations taken reach a likelihood above
$\ell$, is
\begin{align}
n(L_i < \ell) &= \sum_i \mathds{1}\left(L_i < \ell\right) \\
              &= \sum_i \mathds{1}\left(X_i > X(\ell)\right)
\end{align}
The expected value of $n$ given the definition of the algorithm is
\begin{align}
\left<n(L_i < \ell)\right> &= 
              \sum_i \left<\mathds{1}\left(X_i > X(\ell)\right)\right>
\end{align}
